---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PROJ6INLA200618

<!-- badges: start -->
<!-- badges: end -->

The goal of PROJ6INLA200618 is to provide an easy workaround for a bug affecting
`INLA::inla.crs_set_lengthunit` in INLA version 20.06.18,
by overriding the relevant functions with corrected versions.

## Installation

You can install the package from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("finnlindgren/PROJ6INLA200618", ref = "stable")
```
## Example

To use this bug workaround package, first load `INLA`, and then load
`PROJ6INLA200618` (the opposite order will not work):

```{r example}
library(INLA)
library(PROJ6INLA200618)

crs <- sp::CRS("+proj=geocent")
cat(sp::wkt(crs))
cat(sp::wkt(inla.crs_set_lengthunit(crs, "kilometre")))
```
This will display a note about which functions are overridden, and a warning if
the INLA version isn't 20.06.18. In that case, you probably don't need this
workaround package.
